Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-26 WRITEUP/ms.tex
add latex commands to make spacing like Apj

\documentclass[]{emulateapj}
\usepackage{amsmath}
\input{preamble}
\slugcomment{To be submitted to the ApJ}

@@

\title{Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}
%==============================================================================
%                                Front matters
%==============================================================================

@@

We correct for lensing using the median magnification factor $(\mu_{\rm L}\eq5.5)$
from the CO lens models. This yields a \LFIR of $($6.9\pmm3.6$)$\E{11}\,\Lsun.
Assuming a Salpeter initial
mass function \citep{Salpeter55a}, we find a
SFR of (120\pmm63)\,\Msun\,yr\pmOne using the
standard conversion \citep{Kennicutt98a}. 
In the following section, we compare the properties of RXJ1131 
with those reported by C13, which is the largest sample of
ULIRGs at similar redshift (0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements,
to place RXJ1131 in context of existing studies.  
Since C13 adopt a different definition of 
\LFIR (40$-$500\micron)\footnote{We also note that the \fir luminosity in C13 is derived 
based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes.}, we derive the \fir luminosity
following this convention.
This yields \LFIR of $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)$\,\Lsun and 
a SFR of $($150\pmm 70$)$\,\sfrU. 
This implies RXJ1131 is considered a LIRG in regards to their sample, and consequently, 
the SFR of RXJ1131 is lower than the C13 sample (SFR $>$ 200, with an average of 1200).

@@

\subsubsection{Linewidth \& Sizes}
We find that the linewidths for both components (redshifted and blueshifted)
inferred from a double Gaussian fit to the line profile are
consistent with the C13 sample (FWHM of 370\,\kms). Such linewidths are higher
than local ULIRGs (240\,\kms; \citealt[][]{Solomon97a}).
Since C13 do not have resolved observations, we compare the
gas distribution with local ULIRGs. The CO gas in RXJ1131 is
distributed $\sim$6\,kpc in radius across (in
the source plane), which is more extended than the average in the
sample of disk-like ULIRGs studied by \citet{Ueda14a},
who find an average radius of 3.5\,$\pm$\,2.3\,kpc
(with a range from 1.1 kpc to 9.3 kpc).
This indicates that the positive correlation in the linewidth-size relation
holds at intermediate redshifts. Yet we cannot quantify this further
with the data represented in this paper.

@@

% gas-to-dyn ratio
Using the dynamical mass of BLAH (see \Sec{dynamics}), we find
a gas-to-dynamical mass fraction of $f_{\rm gas-dyn}$\,=\,BLAH.
% gas to dust ratio:
Based on the dust mass derived from SED fitting, we find a gas-to-dust ratio of
$f_{\rm gas-dust}$\,=\,70\petm{blah}{blah}, consistent with Combes+13: 206 ?
% Typical local (U)LIRGs are found to have a
%gas-to-dust mass ratio of 200$-$350 (Sanders et al. 1991; Contini
%\& Contini 2003; Seaquist et al. 2004; Wilson et al. 2008).

>>>>

\documentclass[]{emulateapj}
\usepackage{amsmath}
\input{preamble}
\slugcomment{To be submitted to the ApJ}
 \makeatletter
% \renewcommand\normalsize{\@setfontsize\normalsize\@xpt{11.56}}
\renewcommand\normalsize{\@setfontsize\normalsize{10.56}{11.4}}
\makeatother

@@

\title{Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

%==============================================================================
%                                Front matters
%==============================================================================

@@

We correct for lensing using the median magnification factor $(\mu_{\rm L}\eq5.5)$
from the CO lens models. This yields a \LFIR of $($6.9\pmm3.6$)$\E{11}\,\Lsun.
Assuming a Salpeter initial
mass function \citep{Salpeter55a}, we find a
SFR of (120\pmm63)\,\Msun\,yr\pmOne using the
standard conversion \citep{Kennicutt98a}.
To place RXJ1131 in context of existing studies,
we compare its properties
with those reported by C13, which is the largest sample of
IR-luminous galaxy at similar redshift
(0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements.
Since C13 adopt a different definition of
\LFIR (40$-$500\micron)\footnote{We also note that the
\fir luminosity in C13 is derived
based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes.},
we derive the \fir luminosity following this convention.
This yields \LFIR of $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)$\,\Lsun and
a SFR of $($150\pmm 70$)$\,\sfrU.
This implies RXJ1131 is considered a LIRG in regards to their
sample, and consequently,
the SFR of RXJ1131 is lower than that of the C13 sample
(SFR\,$>$\,200, with an average of 1200).

@@

\subsubsection{Linewidth \& Sizes}
We find that the linewidths for both components (redshifted and blueshifted)
inferred from a double Gaussian fit to the line profile are
consistent with the C13 sample (FWHM of 370\,\kms). Such linewidths are higher
than local ULIRGs (240\,\kms; \citealt[][]{Solomon97a}).
Since C13 do not have resolved observations, we compare the
gas distribution with local ULIRGs. The CO gas in RXJ1131 is
distributed $\sim$6\,kpc in radius across (in
the source plane), which is more extended than the average in the
sample of disk-like ULIRGs studied by \citet{Ueda14a},
who find an average radius of 3.5\,$\pm$\,2.3\,kpc
(with a range from 1.1 kpc to 9.3 kpc).
% This also indicates that the positive correlation
% in the linewidth-size relation
% holds at intermediate redshifts. Yet we cannot quantify this further
% with the data represented in this paper.

@@

% gas-to-dyn ratio
Using the dynamical mass of BLAH (see \Sec{dynamics}), we find
a gas-to-dynamical mass fraction of $f_{\rm gas-dyn}$\,=\,BLAH.
% gas to dust ratio:
Based on the dust mass derived from SED fitting, we find a gas-to-dust ratio of
$f_{\rm gas-dust}$\,=\,70\petm{blah}{blah}, which is consistent lower than C13
(who finds 206) sample as well as those of local (U)LIRGs
(200$-$350; Sanders et al. 1991; Contini \& Contini 2003; Seaquist et al. 2004; Wilson et al. 2008).
